\bf Visual Diagnsotics of SAO Models

### 2016-06-27 paper.Rnw
rough outline

\bibliographystyle{asa}
\bibliography{references}

>>>>

\section{Visualizations}

\hh{Some of the visualizations we talked about
\begin{enumerate}
\item visualization of the MCMC process:  movie of individual actors' step-by-step decisions; could be done with the ndtv package, as long as we can get individual steps out of RSiena
\item global picture: 1000 simulated networks + alpha blending should give a pretty good idea of the most important edges
\item global structure + principal components (tensor pca)

\end{enumerate}}
\bibliographystyle{asa}
\bibliography{references}
